---
output: github_document
---
[![Travis build status](https://travis-ci.org/nfox29/photosearcher.svg?branch=master)](https://travis-ci.org/nfox29/photosearcher)
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# photosearcher

The goal of photosearcher is to provide a repeatable methodology for accessing the Flickr API.

Before using the package users should sign uo for an API key from the [Flickr development page](https://www.flickr.com/services/apps/create/).

The Flickr website offers full [API Documentation](https://www.flickr.com/services/api/) for all of its call methods.

## Installation

You can install the released version of photosearcher from github with:

``` r
devtools::install_github("nfox29/photosearcher")
```

## Example

This is a basic example of the main photo_search function:

```{r example}
## photo_search(min_taken = "2019-01-01",
##              max_taken = "2019-01-02",
##              text = "tree",
##              bbox = "-13.623047,47.279229,3.251953,60.630102",
##              has_geo = TRUE)
```
