---
title: "Flickr in research"
output: 
  html_document: 
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)

library(rplos)
library(tidyverse)
library(wordcloud)

get_kw <- function(x) {
  x %>% str_split(",") %>% 
    sapply(function(y) sub(".*/", "", y)) %>% 
    unique()  %>% 
    as.vector() %>% 
    paste(collapse = ",")
}
```

# Flickr papers

To understand how Flickr is currently being use in scientific research we investigated the decipline and scope of articles with the keyword `Flickr` in the [PLoS journals](https://www.plos.org/).

```{r}
plos <- rplos::searchplos(q='flickr', 
                          fl=c('id','publication_date','subject', 'subject_level_1'),
                          limit = 200)$data %>% 
  
  mutate(keywords = map_chr(subject, get_kw),
         subjects = subject_level_1)
```

There are a total of `r nrow(plos)` papers with the keyword `flickr` in the PLoS journals. 

# Subject frequency

To understand the diciplines of science using Flickr we calculated the frequence of papers in each research field:

```{r}
plos %>% 
  pull(subjects) %>% 
  paste(collapse = ",") %>% 
  str_split(",") %>% 
  table %>% 
  as_tibble()
```


# Keyword Wordcloud

To understand what topics are covered by Flickr researches we found the frequency of other keywords attributed to Flickr papers:

```{r}
kws <- plos %>% pull(keywords) %>% paste(collapse = ",") %>% str_split(",") %>% table %>% as.data.frame



wordcloud(words = kws$., freq = kws$Freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```





